{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\ \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal

### 2013-07-21 term-paper/paper.tex
Modified: USP evaluation

  \item[Creating a Markov Logic Network] \hfill \\
  Each atom can be modeled as a node and each first-order clause can be modeled as a feature. This is still not a complete Markov Logical
  Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
  its corredpandant clause. A log-linear distibution $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$is used to model the probability of each clique (configuration of nodes and features).

  \item[Learning the weights of MLN] \hfill \\
  \item[Finding the Best Semantic Parse] \hfill \\
  A semantic parse is a partition of atoms of a QLF, assignment of its head and argument form to a cluster. 
  This can be seen as a structre prediction problem. Given the described MLN and its paramters, inference can
   be done by finding a Maximum A Posterior solution. An exact solution needs a summing over all possible syntactic realizations and
   possible dependency parses, therefor a greedy algorithm to search for a good solution is proposed 
   by the authors.   
\end{description}

\subsection {Evaluation}
\label{ch:evaluation}
sdgdsg

>>>>

  \item[Creating a Markov Logic Network] \hfill \\
  Each atom can be modeled as a node and each first-order clause can be modeled as a feature. This is still not a complete Markov Logical
  Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
  its corredpandant clause. A log-linear distibution 
  $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$
  is used to model the probability of each clique (configuration of nodes and features).
  $Z$ is a normalization factor which its computation is infeasible. $w_i$ is the weight of $i$th formula.
  $n_i$ is number of satisfied atoms and formulas that appeared in the sentence.

  \item[Learning the weights of MLN] \hfill \\
  Given the dependency parse and QLF forms, weights can be learned from data such as the log-likelihood
  of having QLFs given the dependency trees will be maximized. The form of likelihood is:
  $$ L_{\theta}(QLF) = \log{\Sigma_L{P_\theta{(QLF, L)}}}$$ where $L$ is a semantic parse.

  Since the summation of all possible semantic parses is infeasible, a set of additional constraints on the form
  of clauses and also a prior over weights are added to model to make the learning feasible. Their algorithm
  merges any possible two clusters to form a bigger cluster or create a new cluster if either increases the likelihood.
  \item[Finding the Best Semantic Parse] \hfill \\
  A semantic parse is a partition of atoms of a QLF, assignment of its head and argument form to a cluster. 
  This can be seen as a structre prediction problem. Given the described MLN and its paramters, inference can
   be done by finding a Maximum A Posterior solution. An exact solution needs a summing over all possible syntactic realizations and
   possible dependency parses, therefor a greedy algorithm to search for a good solution is proposed 
   by the authors.   
\end{description}

\subsection {Evaluation}
\label{ch:evaluation}
Since USP is the first system for unsupervised semantic parsing, it is compared against other models in a Question/Answering task.
GENIA is an Q/A annotated dataset in medical domain and USP has been shown to find the answers with 88\% precision
which is about 10\% higher than TextRunner and more than 30\% better than DIRT. It is worthwhile to mention that
GENIA is a rather small dataset.

There are two major problems observed by the authors themselves and others for USP.
\begin{itemize}
 \item Same as the other models that we have already seen,
 it doesn't address the separation of antonym relations
 \item It is mentioned in ??? %\cite{Yao} \cite{Titov}
 that USP suffers from using a large memory and therefore low ability to scale to bigger dataset. 
 \end{itemize}
 Two modifications for USP runtime is proposed in ???%\cite{Deep USP} \cite{Titov}.
  In ???  %\cite{Titov}
  it is proposed to use directed graphical models instead of undirected graphs(MLN) to increase the learning and inference speed.
  The result is slighty worse than the original model but it performs faster than USP.
  In ???%\cite{Deep USP} 
  a new representation of the model is given in the framwork of deep learning which yields 
  the same performance but with faster learning algorithm.

  In the next section we will see another model which shows improvement to DIRT, TextRunner and USP 
  and is much more scalable than the former.
